quollr: An R Package for Visalizing 2D Models in High Dimensional Space

### 2024-02-13 paper-quollr.Rmd
Added main workflow for the paper

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE)

```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE)
source("quollr_code.R", local = TRUE)
```

@@

### Compute hexagonal bin configurations

### Generate full hex grid

### Construct the 2D model with different options

### Construct the high-D model with different options

### Generate the triangular mesh

### Compute parameter defaults

#### Shift the hexagonal grid origin

#### Benchmark value to remove the low-density hexagons

#### Benchmark value to remove the long edges

### Model function

### Predict 2D embeddings

### Compute residuals

### Visualizations

#### geom_trimesh

#### coloured_long_edges

#### remove long edges

#### show_langevitour

### 2024-02-13 paper-quollr.tex
Added main workflow for the paper

>>>>

\hypertarget{compute-hexagonal-bin-configurations}{%
\subsubsection{Compute hexagonal bin configurations}\label{compute-hexagonal-bin-configurations}}

\hypertarget{generate-full-hex-grid}{%
\subsubsection{Generate full hex grid}\label{generate-full-hex-grid}}

\hypertarget{construct-the-2d-model-with-different-options}{%
\subsubsection{Construct the 2D model with different options}\label{construct-the-2d-model-with-different-options}}

\hypertarget{construct-the-high-d-model-with-different-options}{%
\subsubsection{Construct the high-D model with different options}\label{construct-the-high-d-model-with-different-options}}

\hypertarget{generate-the-triangular-mesh}{%
\subsubsection{Generate the triangular mesh}\label{generate-the-triangular-mesh}}

\hypertarget{compute-parameter-defaults}{%
\subsubsection{Compute parameter defaults}\label{compute-parameter-defaults}}

\hypertarget{shift-the-hexagonal-grid-origin}{%
\paragraph{Shift the hexagonal grid origin}\label{shift-the-hexagonal-grid-origin}}

\hypertarget{benchmark-value-to-remove-the-low-density-hexagons}{%
\paragraph{Benchmark value to remove the low-density hexagons}\label{benchmark-value-to-remove-the-low-density-hexagons}}

\hypertarget{benchmark-value-to-remove-the-long-edges}{%
\paragraph{Benchmark value to remove the long edges}\label{benchmark-value-to-remove-the-long-edges}}

\hypertarget{model-function}{%
\subsubsection{Model function}\label{model-function}}

\hypertarget{predict-2d-embeddings}{%
\subsubsection{Predict 2D embeddings}\label{predict-2d-embeddings}}

\hypertarget{compute-residuals}{%
\subsubsection{Compute residuals}\label{compute-residuals}}

\hypertarget{visualizations}{%
\subsubsection{Visualizations}\label{visualizations}}

\hypertarget{geom_trimesh}{%
\paragraph{geom\_trimesh}\label{geom_trimesh}}

\hypertarget{coloured_long_edges}{%
\paragraph{coloured\_long\_edges}\label{coloured_long_edges}}

\hypertarget{remove-long-edges}{%
\paragraph{remove long edges}\label{remove-long-edges}}

\hypertarget{show_langevitour}{%
\paragraph{show\_langevitour}\label{show_langevitour}}
